Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex
conflict test
Comments in Sec 2.1 and small notes in Sec 2 and 3

1. Definition of planets: not strictly smaller than 24 \mjup\ any
more? Or still true?

2. Host stars: not only `normal stars' any more?

3. Change on definition of `well-determined' orbital parameters?

@@

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}}

@@

KEPID

@@

EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets'' on exoplanets.org

@@

>>>>

1. Definition of planets: not strictly smaller than 24 \mjup\ any
more? Or still true? We still require smaller than 24 \mjup.

2. Host stars: not only `normal stars' any more? Not any more -
neutron stars are there (at least)! This requirement is completely gone.

3. Change on definition of `well-determined' orbital parameters? No. Still
qualitative, still the same as described in Section~2 of \cite{Wright2011}.

@@

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
here that though we focus on EOD in this Section, the fields apply to
all planets on exoplanets.org.

@@

KEPID: None of EOD planets has KEPID! This is just something we copied
from Exoplanet Archive...

@@

EOD: Planets discovered by radial velocity and transit method are
classified as EOD planets. They have robust orbital parameters such as
PER, ECC, K, OM, and I. \textit{(Sharon's comments: You don't need to
  describe why we include a planet in EOD -- this is covered at the
  beginning of Section~\ref{sec:update} as we discuss the `scope of
  EOD'. Just say what this flag is. Also, right now it includes RV,
  Transit, and also some Timing planets. The first sentence sounds
  like as long as a planet is discovered via RV and transit, it'll be
  in EOD, which is not true, I think.)}

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS-
ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by
methods other than radial velocity and transit. These planets are
categorized as ``Other Planets'' on exoplanets.org. \textit{(Sharon's
  comments: Instead of saying `discovered', we should say `detected'
  -- some planets are detected by these methods but are not
  necessarily discovered by them at the first place. Re-phrase the
  last sentence -- not all of planets with any of these TRUE are in
  `Other Planets', only some are, so maybe just note planets
  discovered by these methods are not necessarily in EOD and direct
  the reader to Section~\ref{sec:kepler} where we talk about `Other
  Planets'. Remember Section~\ref{sec:update} is focuses on EOD
  updates though the fields apply to all planets on
  exoplanets.org. Need to note here that we require the detection to
  be robust, as determined by the QUAlity Control Board of the
  Exoplanet Database, QUACBED.)}

@@

Also add our criteria for vetting IMAGING planets, which can be found
here: http://exoplanets.org/methodology.html; do we have any similar
criteria for Microlensing, timing and astrometry planets? Like mass
cut etc.?
